Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-10 Paper/ms.tex
An abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
Inferring the number of planets $N$ in an exoplanetary system from radial velocity
(RV) data is a challenging task. Typically, the posterior distribution for the
planet parameters is multimodal and may have other awkward features. In
addition, when $N$ is unknown, the marginal likelihood (or evidence), as a
function of $N$, is required. In this paper we propose an alternative
approach using a trans-dimensional Markov Chain Monte Carlo method within
Nested Sampling. We also implement the likelihood function using a look-up
table of pre-computed elliptical orbits.
The posterior distribution for $N$ can be obtained with a
single run, which takes $\sim$ 10 minutes on a typical modern desktop computer.
We apply the method to $\nu$ Oph and XXX, and find moderate evidence
(posterior probability of existence = 70\%) for a third planet around
$\nu$ Oph with an orbital period of 75.7 $\pm$ 1.8 days.
\end{abstract}
